\documentclass[10pt]{article}
\usepackage[medium]{mymemo}
\title{CBASS Testing Plan}
\author{David Carlson \and Sam Flint \and Kaleb Gaar \and Hayden
  Pollmann}

\begin{document}
\maketitle

\section{Introduction}

As with all software systems, CBASS must be tested. This will be done
primarily through blackbox testing performed on the system through a
test runner. Tests will cover all areas of the system completed up to
this point. There areas are defined in the following section.

\section{Requirements}

\subsection{Interfaces}
Testing of the Interfaces (User, Software, and Communications) will
consist of using a browser to load a default survey that demonstrates
constraint functionality (\docsec{3.2.1.3.5}). The survey will then be
completed and exited (\docsec{3.2.2}).

\subsection{Data Collection}
Testing of the Data Collection process will consist of the same
process as described in the previous section, but will occur multiple
times with a different set of responses each time to probe the various
constraint functionalities of the survey (\docsec{3.2.1.3.5}). The
Data Collection will be fully tested once Database testing is also
completed, as this will allow results recorded to be checked for
authenticity.

\subsection{Database}
Testing of the Database will occur after completion of the many
responses of the Data Collection testing. It will consist of pulling
the recorded response data (\docsec{3.2.2.2}) out of the database to
ensure that it was securely stored, and outputting it in a readable
manner. It will also be checked for correctness, completing the Data
Collection testing.

\section{Test Cases}

\subsection{User Authentication}

We will be testing the following (to support \docsec{3.2.1.2}):

\begin{itemize}
\item User authentication by valid password
\item User authentication by invalid password
\item User authentication with invalid username
\item User creation
\item User password change
\end{itemize}

\subsection{Interfaces}

We will be testing the following (to suport \docsec{}):

\begin{itemize}
\item Begin Survey
\item Next question with answer
\item Next question without answer
\item Quit survey early
\item Quit survey
\end{itemize}

\subsubsection{Database}

To support \docsec{3.2.1.3.1--9}:

\begin{itemize}
\item Survey Data Retrieval (name, properties)
\item Survey Question Retrieval
\item Question Response Retrieval
\item Question Constraint Retrieval
\item Survey Creation (name, properties)
\item Survey Question Creation
\item Question Response Creation
\item Question Constraint Retrieval
\item Survey Question Removal
\item Question Response Removal
\item Question Constraint Removal
\end{itemize}

To support \docsec{3.2.2.3.1--4}:

\begin{itemize}
\item Survey Response Insertion
\item Question Response Insertion
\item Question Response Checking (See particularly \docsec{3.2.2.3.2})
\end{itemize}

\subsection{Constraints}

To support in particular \docsec{3.2.2.3.2}:

\begin{itemize}
\item When a FORBID constraint must be applied
\item When a REQUIRES constraint must be applied
\item When a MODIFIES constraint must be applied
\end{itemize}

% \subsection{Data Collection}

\subsection{Data Retrieval}

Not currently implemented at this time.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
